---
title: "Homework5"
author: "Steven Hayden"
date: "September 28, 2017"
output: 
  html_document:
    keep_md: true
---
# Question 1

Import yob2016 and input into a datafram with three columns.

```{r, echo=TRUE}
 setwd("~/GitHub/SMU/Doing_Data_Science_1/Homework/Unit 5")
df<- read.table("yob2016.txt",sep = ";",header = FALSE,col.names = c("FirstName","Gender","AmountofChildren"))
```
Summary
```{r, echo=TRUE}
summary(df)
```
Size
```{r, echo=TRUE}
dim(df)
```
Class
```{r, echo=TRUE}
class(df)
```
finds the row with the misspelled name and removes it

```{r, echo=TRUE}

df[grep('yyy',df$FirstName),]

#removes the bad observation and put the altered df into a new one. 
y2016<-df[-grep('yyy',df$FirstName),]

```

# Question 2

```{r, echo=TRUE}
 setwd("~/GitHub/SMU/Doing_Data_Science_1/Homework/Unit 5")
y2015<- read.table("yob2015.txt",sep = ",",header = FALSE,col.names = c("FirstName","Gender","AmountofChildren"))
tail(y2015,10)

```
###2b
The last 10 names only have 5. There is no variantion in count. 

###2c
merge the two data sets together
```{r, echo=TRUE}
 final<- merge(y2015,df, by.x = c("FirstName","Gender"), by.y =c("FirstName","Gender"),all =  FALSE)
names(final)<-c("FirstName","Gender","AmountofChildren.2015","AmountofChildren.2016")


```
# Question 3
*Adds the count of children together into a new column. Total

*orders the name by most popular for both male and female


```{r, echo=TRUE}
Total<- final$AmountofChildren.2015 + final$AmountofChildren.2016
 final<-cbind(Total,final)
 final<-final[order(-final$Total),c("FirstName","Gender","AmountofChildren.2015","AmountofChildren.2016","Total")]
 head(final,10)

```

*Gives total number of names given in 2015 and 2016

```{r, echo=TRUE} 
sum(Total,na.rm = TRUE)
```

Top ten for Females only and puts it into a new object. The list is then saved to a csv
```{r, echo=TRUE}
setwd("~/GitHub/SMU/Doing_Data_Science_1/Homework/Unit 5")
Girls<-head(final[final$Gender=='F',],10)

write.csv(Girls,"Top 10 girl's names of 2015 and 2016")
```

